\documentclass[12pt,a4paper,titlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{placeins}

\pagestyle{fancy}

\renewcommand{\sectionmark}[1]{%
\markboth{#1}{}}
\fancyhf{} % delete current header and footer
\fancyhead[R]{\bfseries\leftmark}
\fancyfoot[R]{Page \thepage}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\addtolength{\headheight}{2.5pt} % space for the rule

\fancypagestyle{plain}{%
\fancyhead{} % get rid of headers on plain pages
\fancyfoot{} % get rid of headers on plain pages
}

\usepackage[pdftex]{graphicx}
\author{PA Nilsson}
\title{KEEP Quick Start}
\usepackage[pdftex,colorlinks]{hyperref}
\begin{document}
%\maketitle
\FloatBarrier
\section{Installing KEEP}
	\begin{enumerate}

		\item Plug in the network cable to in Internet enabled port, either directly connected to the Internet or behind a router.

		\item Connect the power supply to a mains outlet and plug it into KEEP. KEEP is designed with the intention of being placed close to your router, so the provided ethernet cable is fairly short in order not cause more cable fuss than necessary.

		\item Wait for the LED to start flashing green with heartbeat pattern. This means that KEEP is ready for initialization.
sudo vgremove pool
sudo pvremove /dev/sdd1
sudo wipefs /dev/sdd1

		\item During the order/delivery process for KEEP, you should have received an email with an url to active your unit. The url is in the format of

\begin{small}
https://setup.op-i.me/index.php?unit\_id=41c189de-83e1-47a2-9a6d-a1d61929b01
\end{small}

Follow that link and follow the instruction on screen to complete the setup.

Some of these steps takes a while to complete. It takes a little while before the LED starts to blink green since a lot of inital cryptographic is completed at first boot. Also the checking for existing backups can be a long process if the previous data sets have not been properly shut down. For very large backups, this can unfortunately take hours to complete. But be patient and do not turn off the webbrowser since the system then will be left in an half-configured state.

\end{enumerate}
\begin{quote}
\emph{\textbf{
Note that the master password you select is not stored anywhere and can not be emailed to you if you loose it.
}}

\emph{\textbf{
KEEP is designed to keep your information secure, and all personal information is stored encrypted on KEEP. To accomplish this you will need to provide the password on each restart to unlock KEEP.}}

\emph{\textbf{ Without the password all data is encrypted on the disk and not accessible even if you remove the drive.
}}
\end{quote}


\FloatBarrier
\end{document}
